\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-16 icse/compiler.tex
Revised intro & overview
Updated images

\section{Algorithm Compiler}

@@

In this section, we propose the \textit{algorithm compiler}
that compiles abstract algorithms into \( \ires \) functions
and its overall structure is described in Figure~\ref{fig:algo-compiler}.
Before compiling abstract algorithms,
the tokenizer first tokenizes each abstract algorithm into
a list of tagged tokens. Then, the token parser constructs
syntactic parse tree of the given token list.
Finally, the \( \ires \) function generator constructs the corresponding
\( \ires \) function from the given parse tree.
The parser and the generator is dependent on conversion rules
and we define the general conversion rules for abstract algorithms in
ECMAScript specifications. Like Coq, a proof assistant, we also provide
the \textit{rule generation assistant} to make easy write conversion rules.
It diagnoses root causes of failed parsing tokens
and suggests new conversion rules based on
statistical analysis of algorithm steps that failed to be parsed.

@@

Each parsing rule is written in extended Scala parser combinators.
We modify the meaning of alternative composition operator ( \( | \) ) to collect
all longest matched results. If the parser detects that a step cannot be
parsed with the given parsing rules. It reports that a step is not possible
to be parsed under the given rules into the rule generation assistant.
Moreover, even though the parser could parse a step, it will be also reported
if it could be parsed in not a single but multiple ways.
Each string literal is a token matcher for tokens without any tags and checks
that the token has same string value with the string literal.
The \( \code{varT} \) and \( \code{textT} \) is also token matchers
for token with the tag \( \code{<var>} \) and no tags.
The \( \code{Step} \) and \( \code{Expr} \) are user-defined parsing rules
defined with our extended parser combinators.
Moreover, it supports all helpers functions defined in Scala parser combinators.
For example, the helper function \( \code{repsep(p, q)} \) generates a new
parsing rule that denotes zero or more repetitions of the parsing rule \( \code{p} \)
using another parsing rule \( \code{q} \) as separators.
Finally, the token parser with the above rules parses sub-step \( i \) in the
\( \code{ToPrimitive} \) into the following syntactic parse tree:
\includegraphics[width=0.5\textwidth]{img/parse_tree.png}

@@

To make easy write conversion rules, we support \textit{rule generation assistant}.
It consists of several helper functions to show the specific statistics of
the not yet convertible abstract algorithm steps. It make easy not only construct
conversion rules from the scratch but also update existing conversion rules
for updated specifications. We explain each helper function and how to utilize
it to construct conversion rules.

\subsubsection{Statement format suggestions}

\inred{TODO}

\subsubsection{Fault localization based on \( \tstar \) tokens}

\inred{TODO}

>>>>

\section{Algorithm Compiler}\label{sec:compiler}

@@

In this section, we propose the \textit{algorithm compiler}
that compiles abstract algorithms into \( \ires \) functions
and its overall structure is described in Figure~\ref{fig:algo-compiler}.
Before compiling abstract algorithms,
the tokenizer first tokenizes each abstract algorithm into
a list of tagged tokens. Then, the token parser constructs
syntactic parse tree of the given token list.
Finally, the \( \ires \) function generator constructs the corresponding
\( \ires \) function from the given parse tree.
The parser and the generator is dependent on conversion rules
and we define the general conversion rules for abstract algorithms in
ECMAScript specifications. Like Coq, a proof assistant, we also provide
the \textit{rule generation assistant} to make easy write conversion rules.
It suggests new conversion rules based on
statistical analysis of algorithm steps that failed to be parsed
and also diagnoses root causes of parsing failures.

@@

Each parsing rule is written in extended Scala parser combinators.
We modify the meaning of alternative composition operator ( \( | \) ) to collect
all longest matched results. If the parser detects that a step cannot be
parsed with the given parsing rules. It reports that a step is not possible
to be parsed under the given rules into the rule generation assistant.
Moreover, even though the parser could parse a step, it will be also reported
if it could be parsed in not a single but multiple ways.
Each string literal is a token matcher for tokens without any tags and checks
that the token has same string value with the string literal.
The \( \code{varT} \) and \( \code{textT} \) is also token matchers
for token with the tag \( \code{<var>} \) and no tags.
The \( \code{Step} \) and \( \code{Expr} \) are user-defined parsing rules
defined with our extended parser combinators.
Moreover, it supports all helpers functions defined in Scala parser combinators.
For example, the helper function \( \code{repsep(p, q)} \) generates a new
parsing rule that denotes zero or more repetitions of the parsing rule \( \code{p} \)
using another parsing rule \( \code{q} \) as separators.
Finally, the token parser with the above rules parses sub-step \( i \) in the
\( \code{ToPrimitive} \) into the following syntactic parse tree:
\includegraphics[width=0.5\textwidth]{img/token_ast.png}

@@

\inred{
To make easy write conversion rules, we support \textit{rule generation assistant}.
It consists of two helper functions; the \textit{rule recommender} and
the \textit{fault localizer}. The

It makes easy not only construct conversion rules from the scratch
but also updates existing conversion rules to handle specification updates.
We explain each helper function and how to utilize it to construct conversion rules.

\subsubsection{Statistics Monitor}

TODO

\subsubsection{Fault localizer}

TODO
}
